### 2013-08-21 Tex/chapters/model.tex
kleinere Korrekturen
Bildunterschriften ausführlicher und einige ergänzungen
Cell Methode etwas mehr erläutert.

            \subref{sfig:lunes:def} Lunes of RNG (hatched region) and
                GG (cross hatched region)

@@

    \cite{RNGCell}.\\

@@

@@

@@

            the edge between two distant nodes.\\

@@

>>>>

            \subref{sfig:lunes:def} Lunes, which define where an edge
                exsist, of RNG (hatched region) and GG (cross hatched region)

@@

    \cite{RNGCell} and sketched in Fig.\ \ref{fig:cell}.

@@

        \subfigure[not Connected Nodes][]{

@@

        \subfigure[Connected Nodes][]{

@@

            the edge between two distant nodes. The nodes inside the
            other 8 marked cells do not have to be tested anymore.\\

@@

    Here the number of cells equals the number of nodes.
